Cloud-SAP: Self-adaptive platform for scaling users' application deployed in a federation of cloud computing environments

### 2013-09-14 article/article.tex
Change table styles
Add the state-of-the-art in cc providers in the article

\section{Who is Who in cloud provisioning}

\begin{table*}[ht]
  \renewcommand{\arraystretch}{2}
  \begin{tabular}{p{2.5cm} | *{3}{C}}
    \multicolumn{1}{c}{} & \textbf{Memory} & \textbf{CPU} & \textbf{Disk} \\ \hline

@@

\begin{table*}[ht]
  \renewcommand{\arraystretch}{2}
\begin{tabular}{ l | c | c | c c }
  \hline 
  \multicolumn{1}{l}{} & \multicolumn{1}{l}{\textbf{Horizontal scaling}} & \multicolumn{1}{l}{\textbf{Vertical scaling}} & \textbf{Application / resource tuning} \\ \hline

  \multicolumn{1}{l}{\textbf{Infrastructure provider}} & \multicolumn{4}{ l }{} \\ \hline

Carina & \checkmark & $\times$ & $\times$ & \\ \hline

OneFlow & \checkmark & $\times$ & $\times$ & \\ \hline

AWS EC2 & \checkmark & $\times$ & $\times$ & \\ \hline

\multicolumn{1}{l}{\textbf{Platform provider}} & \multicolumn{4}{ l }{} \\ \hline

CloudFoundry & $\times$ & $\times$ & $\times$  &\\ \hline

OpenShift & \checkmark & $\times$ & $\times$  &\\ \hline

AppEngine & \checkmark & $\times$ & $\times$  &\\ \hline

Azure & \checkmark & $\times$ & $\times$  &\\ \hline

Heroku & \checkmark & $\times$ & $\times$ & \\ \hline
\end{tabular}

@@

\section{Architecture of SAP-Cloud}

>>>>

\paragraph{Hypervisors} Being able to scale resources vertically requires hypervisors to have such possibilities. Table \ref{tab:hypervisors-resizing} presents resizing capabilities of common hypervisors.

\begin{table*}[ht]
  \renewcommand{\arraystretch}{2}
  \begin{tabular}{p{4cm} | *{3}{C}}
    \multicolumn{1}{c}{} & \textbf{Memory} & \textbf{CPU} & \textbf{Disk} \\ \hline

@@

\section{Who is Who in cloud provisioning}
In the context of this article, the main point of interest are providers which offer features related to resource management, monitoring and utilization. In general, current key providers include Amazon \emph{Web Services}, \emph{Microsoft Azure}, Google \emph{AppEngine} and \emph{Heroku}. Despite not all of them operate on the same level of abstraction, it is possible to compare them as they expose functionalities which can be classified as PaaS. For example, on top of its infrastructure services, Amazon has such products as \emph{Elastic Load Balancer}, \emph{Cloud Watch} and \emph{Auto Scaling} which, to some extent, matches our needs.

Table \ref{tab:cloud-providers-scaling} presents comparison of some Cloud providers with the emphasis on their scaling capabilities. Interestingly, all of them are focused solely on horizontal scaling, ignoring advantages offered by a fine-grained approach to scaling that leverage scaling up and application tuning.

\begin{table*}[ht]
  \renewcommand{\arraystretch}{2}
  \begin{tabular}{ p{4cm} | C | C | C }
  \hline 
  \multicolumn{1}{l}{} & \multicolumn{1}{l}{\textbf{Horizontal scaling}} & \multicolumn{1}{l}{\textbf{Vertical scaling}} & \textbf{Application / resource tuning} \\ \hline

  \multicolumn{1}{l}{\textbf{Infrastructure provider}} & \multicolumn{3}{ l }{} \\ \hline

Carina & \checkmark & $\times$ & $\times$ \\ \hline

OneFlow & \checkmark & $\times$ & $\times$ \\ \hline

AWS EC2 & \checkmark & $\times$ & $\times$ \\ \hline

\multicolumn{1}{l}{\textbf{Platform provider}} & \multicolumn{3}{ l }{} \\ \hline

CloudFoundry & $\times$ & $\times$ & $\times$  \\ \hline

OpenShift & \checkmark & $\times$ & $\times$  \\ \hline

AppEngine & \checkmark & $\times$ & $\times$  \\ \hline

Azure & \checkmark & $\times$ & $\times$  \\ \hline

Heroku & \checkmark & $\times$ & $\times$ \\ \hline
\end{tabular}

@@

\section{Adaptivity}
\section{Architecture of SAP-Cloud}
